---
title: "Honors Thesis_Main Study"
author: "Qilin Zhang"
date: "2/6/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
HT_MTurk <- read_csv("D:/Psychology Research/Data/HT_MTurk.csv")
```

```{r}
#Packages
library(dplyr)
library(Hmisc)
library(tidyr)
library(ggplot2)
library(psych)
library(summarytools)
library(car)
library(psy)
library(openxlsx)
```


## <- HT2_Raw[c(-1,-2),]
HT_MC_Main <- subset(HT_MC_Main, as.numeric(HT_MC_Main$Progress)>=95)
HT_MC_Main$Condition <- ifelse((is.na(HT_MC_Main$Self_S_reflect_4)== FALSE),"self",(ifelse(is.na(HT_MC_Main$Other_O_reflect_4)== FALSE, "other", "self&other")))
freq(HT_MC_Main$Condition)## (no use so far)
Data cleaning Start:

```{r}
#Data Cleaning
##filtering unqualified data
HT2 <- HT_MTurk
HT2$X500<- NULL
HT2 <- HT2[c(-1,-2),]
HT2_Raw <- HT2
#HT2 <- subset(HT2, as.numeric(HT2_Raw$`Duration (in seconds)`)>=291)
HT2 <- subset(HT2, as.numeric(HT2$Progress)>=95)
HT2 <- subset(HT2,HT2$Prosocial_Intent_19=="Neither likely nor unlikely")
HT2 <- subset(HT2,HT2$Social_Desirability_17=="FALSE")
##Labeling condition
HT2$Condition <- ifelse((is.na(HT2$`Timing_self_Page Submit`)== FALSE),"self",(ifelse(is.na(HT2$`Timing_Other_Page Submit`)== FALSE, "other", (ifelse(is.na(HT2$`Timing_O&S_Page Submit`)== FALSE, "self&other","nothing")))))
HT2_1 <- subset(HT2, as.numeric(HT2$`Timing_Other_Page Submit`)>=25)
HT2_1 <- subset(HT2_1,(is.na(HT2_1$Comprehension_check)== FALSE))
HT2_2 <- subset(HT2, as.numeric(HT2$`Timing_self_Page Submit`)>=25)
HT2_2 <- subset(HT2_2,(is.na(HT2_2$Comprehension_check)== FALSE))
HT2_3 <- subset(HT2, as.numeric(HT2$`Timing_O&S_Page Submit`)>=25)
HT2_3 <- subset(HT2_3,(is.na(HT2_3 $Comprehension_check)== FALSE))
HT2_4 <- subset(HT2, HT2$Condition6 == "nothing" )
##Clean the data from robots
HT2_4 <- subset(HT2_4,(is.na(HT2_4$Social_Desirability_1)== FALSE))
HT2_4 <- subset(HT2_4,(is.na(HT2_4$COVID_Stress_1)== FALSE))

HT2 <- rbind.data.frame(HT2_1,HT2_2,HT2_3)

# <- rbind.data.frame(HT2_1,HT2_2,HT2_3,HT2_4)


```
##exclude all people who have read the message
HT2 <-subset(HT2, (ifelse(is.na(HT2$Read_before)==TRUE, TRUE, (ifelse(HT2$Read_before!="Yes", TRUE, FALSE)))))

Re-code Values
  For Manipulation Check

```{r}

HT2$Vol_Benefits_Uni_S <- as.numeric(factor((HT2$Vol_Benefits_Uni_S),
levels=c("Strongly disagree","Disagree","Somewhat disagree","Neither agree nor disagree","Somewhat agree","Agree","Strongly agree"),
labels=c("1","2","3","4","5","6","7")))

HT2$Vol_Benefits_Uni_O <- as.numeric(factor((HT2$Vol_Benefits_Uni_O),
levels=c("Strongly disagree","Disagree","Somewhat disagree","Neither agree nor disagree","Somewhat agree","Agree","Strongly agree"),
labels=c("1","2","3","4","5","6","7")))

HT2$Vol_Benefits_Bi <- as.numeric(as.character(factor((HT2$Vol_Benefits_Bi),
levels=c("Benefited the students extremely more than the Matthew","Benefited the students moderately more than the Matthew","Benefited the students slightly more than the Matthew","Benefited the students and Matthew equally","Benefited Matthew slightly more than the students","Benefited the Matthew moderately more than the students","Benefited Matthew extremely more than the students"),
labels=c("1","2","3","4","5","6","7"))))

HT2$Vol_Intent_S <- as.numeric(factor((HT2$Vol_Intent_S),
levels=c("Strongly disagree","Disagree","Somewhat disagree","Neither agree nor disagree","Somewhat agree","Agree","Strongly agree"),
labels=c("1","2","3","4","5","6","7")))

HT2$Vol_Intent_O <- as.numeric(factor((HT2$Vol_Intent_O),
levels=c("Strongly disagree","Disagree","Somewhat disagree","Neither agree nor disagree","Somewhat agree","Agree","Strongly agree"),
labels=c("1","2","3","4","5","6","7")))
```

  For main study

```{r}
####Social desirability

SD_Recode <- function (subject){
subject <- (as.numeric(as.character(factor(subject,
levels= c("TRUE","FALSE"),
labels = c(1,0)))))
}

SD_Reverse_Recode <- function (subject){
subject <- (as.numeric(as.character(factor(subject,
levels= c("TRUE","FALSE"),
labels = c(0,1)))))
}

HT2$Social_Desirability_1 <- SD_Reverse_Recode(HT2$Social_Desirability_1)
HT2$Social_Desirability_5 <- SD_Reverse_Recode(HT2$Social_Desirability_5)
HT2$Social_Desirability_6 <- SD_Reverse_Recode(HT2$Social_Desirability_6)
HT2$Social_Desirability_10 <- SD_Reverse_Recode(HT2$Social_Desirability_10)
HT2$Social_Desirability_14 <- SD_Reverse_Recode(HT2$Social_Desirability_14)
HT2$Social_Desirability_16 <- SD_Reverse_Recode(HT2$Social_Desirability_16)

HT2$Social_Desirability_2 <- SD_Recode(HT2$Social_Desirability_2)
HT2$Social_Desirability_3 <- SD_Recode(HT2$Social_Desirability_3)
HT2$Social_Desirability_4 <- SD_Recode(HT2$Social_Desirability_4)
HT2$Social_Desirability_7 <- SD_Recode(HT2$Social_Desirability_7)
HT2$Social_Desirability_8 <- SD_Recode(HT2$Social_Desirability_8)
HT2$Social_Desirability_9 <- SD_Recode(HT2$Social_Desirability_9)
HT2$Social_Desirability_11 <- SD_Recode(HT2$Social_Desirability_11)
HT2$Social_Desirability_12 <- SD_Recode(HT2$Social_Desirability_12)
HT2$Social_Desirability_13 <- SD_Recode(HT2$Social_Desirability_13)
HT2$Social_Desirability_15 <- SD_Recode(HT2$Social_Desirability_15)

HT2$Social_Desirability_Score <- (HT2$Social_Desirability_1+HT2$Social_Desirability_2+HT2$Social_Desirability_3+HT2$Social_Desirability_4+HT2$Social_Desirability_5+HT2$Social_Desirability_6+HT2$Social_Desirability_7+HT2$Social_Desirability_8+HT2$Social_Desirability_9+HT2$Social_Desirability_10+HT2$Social_Desirability_11+HT2$Social_Desirability_12+HT2$Social_Desirability_13+HT2$Social_Desirability_14+HT2$Social_Desirability_15+HT2$Social_Desirability_16)
```


```{r}
####COVID stress

HT2$COVID_Stress_1 <- as.numeric(factor((HT2$COVID_Stress_1),
levels=c("Not impactful at all (1)","2","3","4","Extremely impactful (5)"),
labels=c("1","2","3","4","5")))
```


```{r}
####Volunteer intention
HT2$Vol_Intent_1 <- as.numeric(HT2$Vol_Intent_50)
HT2$Vol_Intent_2 <- as.numeric(HT2$Vol_Intent_51)

#####Combined Vol intention
HT2$Vol_intent_combined <- (as.numeric(HT2$Vol_Intent_50)+as.numeric(HT2$Vol_Intent_51))


#cor(HT2$Vol_Intent_1,HT2$Vol_Intent_2)
```

#####Next year
HT2$Vol_Intent_1 <- as.numeric(factor((HT2$Vol_Intent_1),
levels=c("Extremely unlikely","Moderately unlikely","Slightly unlikely","Neither likely nor unlikely","Slightly likely","Moderately likely","Extremely likely"),
labels=c("1","2","3","4","5","6","7")))

#####three years
HT2$Vol_Intent_2 <- as.numeric(factor((HT2$Vol_Intent_2),
levels=c("Extremely unlikely","Moderately unlikely","Slightly unlikely","Neither likely nor unlikely","Slightly likely","Moderately likely","Extremely likely"),
labels=c("1","2","3","4","5","6","7")))

```{r}
####PBIS
#(Comfort someone I know after they experience a hardship`)
HT2$PBIS_1 <- as.numeric(factor((HT2$PBIS_1),
levels=c("Extremely unlikely","Moderately unlikely","Slightly unlikely","Neither likely nor unlikely","Slightly likely","Moderately likely","Extremely likely"),
labels=c("1","2","3","4","5","6","7")))

#(Help a stranger find something they lost, like their key or a pet)
HT2$PBIS_2 <- as.numeric(factor((HT2$PBIS_2),
levels=c("Extremely unlikely","Moderately unlikely","Slightly unlikely","Neither likely nor unlikely","Slightly likely","Moderately likely","Extremely likely"),
labels=c("1","2","3","4","5","6","7")))

#(Help care for a sick friend or relative)
HT2$PBIS_3 <- as.numeric(factor((HT2$PBIS_3),
levels=c("Extremely unlikely","Moderately unlikely","Slightly unlikely","Neither likely nor unlikely","Slightly likely","Moderately likely","Extremely likely"),
labels=c("1","2","3","4","5","6","7")))

#(Assist a stranger with a small task (e.g., help carry groceries, watch their things while they use the restroom))
HT2$PBIS_4 <- as.numeric(factor((HT2$PBIS_4),
levels=c("Extremely unlikely","Moderately unlikely","Slightly unlikely","Neither likely nor unlikely","Slightly likely","Moderately likely","Extremely likely"),
labels=c("1","2","3","4","5","6","7")))

#####Combined PBIS
HT2$PBIS_score<-(HT2$PBIS_1+HT2$PBIS_2+HT2$PBIS_3+HT2$PBIS_4)
```


```{r}
####Prosocial intention

Pro_intent_Recode <- function (subject){
subject <- as.numeric(factor((subject),
levels=c("Extremely unlikely","Moderately unlikely","Slightly unlikely","Neither likely nor unlikely","Slightly likely","Moderately likely","Extremely likely"),
labels=c("1","2","3","4","5","6","7")))
}

#(Give directions to a stranger)
HT2$Prosocial_Intent_1 <- Pro_intent_Recode(HT2$Prosocial_Intent_1)

#(Made change for a stranger)
HT2$Prosocial_Intent_2 <- Pro_intent_Recode(HT2$Prosocial_Intent_2)

#(Give money to a stranger who needed it)
HT2$Prosocial_Intent_3 <- Pro_intent_Recode(HT2$Prosocial_Intent_3)

#(Give money to a stranger who asked me for it)
HT2$Prosocial_Intent_4 <- Pro_intent_Recode(HT2$Prosocial_Intent_4)

#(Give money to charity)
HT2$Prosocial_Intent_5 <- Pro_intent_Recode(HT2$Prosocial_Intent_5)

#(Donate goods or clothes to a charity)
HT2$Prosocial_Intent_6 <- Pro_intent_Recode(HT2$Prosocial_Intent_6)

#(Donate blood)
HT2$Prosocial_Intent_7 <- Pro_intent_Recode(HT2$Prosocial_Intent_7)

#(Do volunteer work for a charity)
HT2$Prosocial_Intent_8 <- Pro_intent_Recode(HT2$Prosocial_Intent_8)

#(Help carry a stranger's belongings (e.g., books, parcels, etc.))
HT2$Prosocial_Intent_9 <- Pro_intent_Recode(HT2$Prosocial_Intent_9)

#(Delay an elevator and hold the door open for a stranger.)
HT2$Prosocial_Intent_10 <- Pro_intent_Recode(HT2$Prosocial_Intent_10)

#(Allow someone to go ahead of me in a line (e.g., supermarket, copying machine, etc.))
HT2$Prosocial_Intent_11 <- Pro_intent_Recode(HT2$Prosocial_Intent_11)

#(Give a stranger a lift in my car)
HT2$Prosocial_Intent_12 <- Pro_intent_Recode(HT2$Prosocial_Intent_12)

#(Let a neighbor whom I didn't know too well borrow an item of some value (e.g.,. I tools, a dish, etc.))
HT2$Prosocial_Intent_13 <- Pro_intent_Recode(HT2$Prosocial_Intent_13)

#(Buy 'charity' Christmas cards deliberately because I knew it was for a good cause)
HT2$Prosocial_Intent_14 <- Pro_intent_Recode(HT2$Prosocial_Intent_14)

#(Help a classmate who I did not know that well with a homework assignment when my knowledge was greater than his or hers)
HT2$Prosocial_Intent_15 <- Pro_intent_Recode(HT2$Prosocial_Intent_15)

#(Voluntarily look after a neighbor's pets or children without being paid for it)
HT2$Prosocial_Intent_16 <- Pro_intent_Recode(HT2$Prosocial_Intent_16)

#(Offer to help a handicapped or elderly stranger across a street)
HT2$Prosocial_Intent_17 <- Pro_intent_Recode(HT2$Prosocial_Intent_17)

#(Point out a clerk's error (in a bank, at the supermarket) in undercharging me for an item)
HT2$Prosocial_Intent_18 <- Pro_intent_Recode(HT2$Prosocial_Intent_18)

#####Prosocial Intention combined
HT2$Pro_Intent_Score <- (HT2$Prosocial_Intent_1+HT2$Prosocial_Intent_2+HT2$Prosocial_Intent_3+HT2$Prosocial_Intent_4+HT2$Prosocial_Intent_5+HT2$Prosocial_Intent_6+HT2$Prosocial_Intent_7+HT2$Prosocial_Intent_8+HT2$Prosocial_Intent_9+HT2$Prosocial_Intent_10+HT2$Prosocial_Intent_11+HT2$Prosocial_Intent_12+HT2$Prosocial_Intent_13+HT2$Prosocial_Intent_14+HT2$Prosocial_Intent_15+HT2$Prosocial_Intent_16+HT2$Prosocial_Intent_17+HT2$Prosocial_Intent_18)
```


```{r}
####Prosocial behavior measure

HT2$Pro_beh_2 <- ifelse(is.na(HT2$Pro_beh_2)==TRUE, 0, (ifelse((HT2$Pro_beh_2=="Yes"), 1, 0)))

HT2$Prosocial_Beh <- HT2$Pro_beh_2

HT2$Prosocial_Beh <- ifelse((HT2$Pro_beh_2==0), 0, (ifelse((HT2$Pro_beh_Validation=="Yes"), 1,NA)))


```

Data cleaning ends
Manipulation Check_Descriptive Analysis Starts

```{r}
#Descriptive Analysis

##Participants' by condition
freq(HT2$Condition)

##Volunteer benefit_self or others_Forced choice
freq(HT2$Vol_Benefits_forced)

##Volunteer benefits and intentions
###Volunteer benefits_others
descr(as.numeric(HT2$Vol_Benefits_Uni_O))
###Volunteer benefits_self
descr(as.numeric(HT2$Vol_Benefits_Uni_S))
###Volunteer Intention_benefiting self
descr(as.numeric(HT2$Vol_Intent_S))
###Volunteer Intention_benefiting others
descr(as.numeric(HT2$Vol_Intent_O))
###Volunteer benefit_self or others
descr(HT2$Vol_Benefits_Bi)

##Page submit time 
### in Raw data
descr(as.numeric(HT2_Raw$`Timing_O&S_Page Submit`))
descr(as.numeric(HT2_Raw$`Timing_self_Page Submit`))
descr(as.numeric(HT2_Raw$`Timing_Other_Page Submit`))

### in filtered data 
descr(as.numeric(HT2$`Timing_O&S_Page Submit`))
descr(as.numeric(HT2$`Timing_self_Page Submit`))
descr(as.numeric(HT2$`Timing_Other_Page Submit`))

#Should we add an ANOVA for testing whether participants spent more time in one message then the others?

```

Manipulation Check_Descriptive Analysis ends
Manipulation Check_Inferential Analysis Starts

```{r}
#Inferential Analysis_Manipulation check
Anova(lm(Vol_Intent_O~Condition, data=HT2))
tapply(HT2$Vol_Intent_O, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$Vol_Intent_O, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(Vol_Intent_O~Condition, data=HT2)))

Anova(lm(Vol_Intent_S~Condition, data=HT2))
tapply(HT2$Vol_Intent_S, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$Vol_Intent_S, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(Vol_Intent_S~Condition, data=HT2)))

Anova(lm(Vol_Benefits_Bi~Condition, data=HT2))
tapply(HT2$Vol_Benefits_Bi, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$Vol_Benefits_Bi, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(Vol_Benefits_Bi~Condition, data=HT2)))

Anova(lm(Vol_Benefits_Uni_O~Condition, data=HT2))
tapply(HT2$Vol_Benefits_Uni_O, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$Vol_Benefits_Uni_O, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(Vol_Benefits_Uni_O~Condition, data=HT2)))

Anova(lm(Vol_Benefits_Uni_S~Condition, data=HT2))
tapply(HT2$Vol_Benefits_Uni_S, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$Vol_Benefits_Uni_S, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(Vol_Benefits_Uni_S~Condition, data=HT2)))

chisq.test(HT2$Condition,HT2$Vol_Benefits_forced)
tapply(HT2$Vol_Benefits_forced, INDEX =HT2$Condition, FUN = freq)


#cro(HT2$Vol_Benefits_forced, HT2$Condition)
#cro_cpct(HT2$Vol_Benefits_forced, HT2$Condition)
```
```{r}

ggplot(HT2, aes(y = Vol_Benefits_Uni_O,x = Condition),)+
  geom_boxplot()+
  labs(y='Vol_Benefts_Uni_O', x='condition')

ggplot(HT2, aes(y = Vol_Benefits_Uni_S,x = Condition),)+
  geom_boxplot()+
  labs(y='Vol_Benefts_Uni_S', x='condition')

ggplot(HT2, aes(y = Vol_Benefits_Bi,x = Condition),)+
  geom_boxplot()+
  labs(y='Vol_Benefts_Bi', x='condition')

ggplot(HT2, aes(y = Vol_Intent_O,x = Condition),)+
  geom_boxplot()+
  labs(y='Vol_Intent_O', x='condition')

ggplot(HT2, aes(y = Vol_Intent_S,x = Condition),)+
  geom_boxplot()+
  labs(y='Vol_Intent_S', x='condition')


ggplot(HT2, aes(x = Vol_Intent_S),)+
  geom_density()
ggplot(HT2, aes(x = Vol_Intent_O),)+
  geom_density()


ggplot(HT2, aes(x = Vol_Benefits_Uni_O,y = Condition),)+
  geom_boxplot()+
  labs(y='Vol_Benefts_Uni_O', x='condition')

plot_O <- cbind.data.frame(HT2$Vol_Benefits_Uni_O,HT2$Condition)
plot_O$variable <- ifelse(is.na(HT2$Vol_Benefits_Uni_O)==TRUE, NA, "Other benefit")
names(plot_O) <- c("Vol_Benefits","Condition","variable")

plot_S <- cbind.data.frame(HT2$Vol_Benefits_Uni_S,HT2$Condition)
plot_S$variable <- ifelse(is.na(HT2$Vol_Benefits_Uni_S)==TRUE, NA, "Self benefit")
names(plot_S) <- c("Vol_Benefits","Condition","variable")


Plot <- rbind(plot_O,plot_S)

    
```
Manipulation check ends
Coding for the main effects starts
```{r}
##Social_Desirability
descr(as.numeric(HT2$Social_Desirability_Score))
ggplot(HT2, aes(x = Social_Desirability_Score),)+
  geom_density()

##COVID stress
descr(as.numeric(HT2$COVID_Stress_1))
ggplot(HT2, aes(x = COVID_Stress_1),)+
  geom_density()

##Volunteer intention
descr(as.numeric(HT2$Vol_intent_combined))
ggplot(HT2, aes(x = Vol_intent_combined),)+
  geom_density()


##PBIS
descr(as.numeric(HT2$PBIS_score))
ggplot(HT2, aes(x = PBIS_score),)+
  geom_density()
hist(HT2$PBIS_score)

##Prosocial intention
descr(as.numeric(HT2$Pro_Intent_Score))
ggplot(HT2, aes(x = Pro_Intent_Score),)+
  geom_density()
```
HT2$Vol_intent_combined_High_Low <- quantileCut (HT2$Vol_intent_combined, 2)
table(HT2$Vol_intent_combined )
HT2$Vol_intent_combined_High_Low <- factor(HT2$Vol_intent_combined_High_Low,
levels= c("(5.99,12]", "(12,14]"),
labels = c("Low","High" ))
table(HT2$Vol_intent_combined_High_Low )


cro(HT2$Vol_intent_combined,HT2$Condition)
cro_cpct(HT2$Vol_intent_combined,HT2$Condition)


cro_cpct(HT2$Condition,HT2$Vol_intent_combined)

```{r}
##Demographics
###Age
descr(as.numeric(HT2$Dem_Age))

###Sex
freq(HT2$Dem_Bio_Sex)

###Gender
freq(HT2$Dem_Gen_ID)

###Race
freq(HT2$Dem_Race)
freq(HT2$Dem_Race_6_TEXT)

###Gender
freq(HT2$Dem_Gen_ID)

```

```{r}
#Inferential Analysis
## Social desirability
SD_cronbach <- data.frame(HT2$Social_Desirability_1,HT2$Social_Desirability_2,HT2$Social_Desirability_3,HT2$Social_Desirability_4,HT2$Social_Desirability_5,HT2$Social_Desirability_6,HT2$Social_Desirability_7,HT2$Social_Desirability_8,HT2$Social_Desirability_9,HT2$Social_Desirability_10,HT2$Social_Desirability_11,HT2$Social_Desirability_12,HT2$Social_Desirability_13,HT2$Social_Desirability_14,HT2$Social_Desirability_15,HT2$Social_Desirability_16)
cronbach(SD_cronbach)

Anova(lm(Social_Desirability_Score~Condition, data=HT2))
tapply(HT2$Social_Desirability_Score, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$Social_Desirability_Score, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(Social_Desirability_Score~Condition, data=HT2)))

#COVID stress
Anova(lm(COVID_Stress_1~Condition, data=HT2))
tapply(HT2$COVID_Stress_1, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$COVID_Stress_1, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(COVID_Stress_1~Condition, data=HT2)))

##Volunteer intention
Vol_Intent_cronbach <- data.frame(HT2$Vol_Intent_1, HT2$Vol_Intent_2)
cronbach(Vol_Intent_cronbach)

Anova(lm(Vol_intent_combined~Condition, data=HT2))
tapply(HT2$Vol_intent_combined, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$Vol_intent_combined, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(Vol_intent_combined~Condition, data=HT2)))

Anova(lm(Vol_Intent_1~Condition, data=HT2))
tapply(HT2$Vol_Intent_1, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$Vol_Intent_1, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(Vol_Intent_1~Condition, data=HT2)))

Anova(lm(Vol_Intent_2~Condition, data=HT2))
tapply(HT2$Vol_Intent_2, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$Vol_Intent_2, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(Vol_Intent_2~Condition, data=HT2)))

t.test(HT2$Vol_Intent_1,HT2$Vol_Intent_2,alternative = c("two.sided"),paired = TRUE,conf.level = 0.95)

##PBIS
Anova(lm(PBIS_score~Condition, data=HT2))
tapply(HT2$PBIS_score, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$PBIS_score, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(PBIS_score~Condition, data=HT2)))

PBIS_cronbach <- data.frame(HT2$PBIS_1,HT2$PBIS_2,HT2$PBIS_3,HT2$PBIS_4)
cronbach(PBIS_cronbach)

##Prosocial intention
Anova(lm(Pro_Intent_Score~Condition, data=HT2))
tapply(HT2$Pro_Intent_Score, INDEX =HT2$Condition, FUN = mean)
tapply(HT2$Pro_Intent_Score, INDEX =HT2$Condition, FUN = sd)
TukeyHSD(aov(lm(Pro_Intent_Score~Condition, data=HT2)))

Prosocial_beh_cronbach <- data.frame(HT2$Prosocial_Intent_1,HT2$Prosocial_Intent_2,HT2$Prosocial_Intent_3,HT2$Prosocial_Intent_4,HT2$Prosocial_Intent_5,HT2$Prosocial_Intent_6,HT2$Prosocial_Intent_7,HT2$Prosocial_Intent_8,HT2$Prosocial_Intent_9,HT2$Prosocial_Intent_10,HT2$Prosocial_Intent_11,HT2$Prosocial_Intent_12,HT2$Prosocial_Intent_13,HT2$Prosocial_Intent_14,HT2$Prosocial_Intent_15,HT2$Prosocial_Intent_16,HT2$Prosocial_Intent_17,HT2$Prosocial_Intent_18)
cronbach(Prosocial_beh_cronbach)



##Prosocial behavior
chisq.test(HT2$Condition,HT2$Prosocial_Beh)
tapply(HT2$Prosocial_Beh, INDEX =HT2$Condition, FUN = freq)
```


```{r}
##Social desirability and prosociality

Regression_shortcut <- function (x,y){
  z <- lm(x~y)
  a <- summary(z)
  b <- confint(z)
  return (list(a,b))
}

###Volunteer intention
Vol_intent_SD_regression <- lm(Social_Desirability_Score~Vol_intent_combined, data =HT2)
summary(Vol_intent_SD_regression)
confint(Vol_intent_SD_regression, level = 0.95)

Vol_intent_SD_regression_1 <- lm(Social_Desirability_Score~Vol_Intent_1, data =HT2)
summary(Vol_intent_SD_regression_1)
confint(Vol_intent_SD_regression_1, level = 0.95)

Vol_intent_SD_regression_2 <- lm(Social_Desirability_Score~Vol_Intent_2, data =HT2)
summary(Vol_intent_SD_regression_2)
confint(Vol_intent_SD_regression_2, level = 0.95)
 
###PBIS
PBIS_SD_regression <- lm(Social_Desirability_Score~PBIS_score, data =HT2)
summary(PBIS_SD_regression)
confint(PBIS_SD_regression, level = 0.95)

###Prosocial behavior
Pro_intent_SD_regression <- lm(Social_Desirability_Score~Pro_Intent_Score, data =HT2)
summary(Pro_intent_SD_regression)
confint(Pro_intent_SD_regression, level = 0.95)
```


```{r}
##COVID stress and prosociality
###Volunteer intention
Vol_intent_COVID_regression <- lm(COVID_Stress_1~Vol_intent_combined, data =HT2)
summary(Vol_intent_COVID_regression)
confint(Vol_intent_COVID_regression, level = 0.95)

Vol_intent_COVID_regression_1 <- lm(COVID_Stress_1~Vol_Intent_1, data =HT2)
summary(Vol_intent_COVID_regression_1)
confint(Vol_intent_COVID_regression_1, level = 0.95)

Vol_intent_COVID_regression_2 <- lm(COVID_Stress_1~Vol_Intent_2, data =HT2)
summary(Vol_intent_COVID_regression_2)
confint(Vol_intent_COVID_regression_2, level = 0.95)

###PBIS
PBIS_COVID_regression <- lm(COVID_Stress_1~PBIS_score, data =HT2)
summary(PBIS_COVID_regression)
confint(PBIS_COVID_regression, level = 0.95)

###Prosocial behavior
Pro_intent_COVID_regression <- lm(COVID_Stress_1~Pro_Intent_Score, data =HT2)
summary(Pro_intent_COVID_regression)
confint(Pro_intent_COVID_regression, level = 0.95)
```


```{r}
##PBIS&Prosocial behavior
PBIS_Pro_Intent_regression <- lm(Pro_Intent_Score~PBIS_score, data =HT2)
summary(PBIS_Pro_Intent_regression)
confint(PBIS_Pro_Intent_regression, level = 0.95)
plot(PBIS_Pro_Intent_regression)

t.test(Pro_Intent_Score~Prosocial_Beh,alternative = c("less"), data= HT2)
t.test(PBIS_score~Prosocial_Beh, alternative = c("less"),data= HT2)

```


```{r}
##Social desirability and prosociality (graph)
###Volunteer intention
ggplot(HT2, aes(x = Social_Desirability_Score, y = Vol_intent_combined),)+
  geom_point()+
  geom_abline()

```




```{r}

### Joshua work April 4th


Inter_CorrData<-data.frame(HT2$Social_Desirability_Score, HT2$COVID_Stress_1,HT2$Vol_intent_combined,HT2$Vol_Intent_1,HT2$Vol_Intent_2,HT2$PBIS_score,HT2$Pro_Intent_Score )
Thesis_InterCor <- rcorr(as.matrix(Inter_CorrData,type=c("pearson")))
write.xlsx(as.data.frame(Thesis_InterCor$r), file  = "Inter_CorrData.csv" )

Anova(lm(HT2$Vol_intent_combined~HT2$Condition+HT2$Social_Desirability_Score))
Anova(lm(HT2$Vol_Intent_1~HT2$Condition+HT2$Social_Desirability_Score))
Anova(lm(HT2$Vol_Intent_2~HT2$Condition+HT2$Social_Desirability_Score)) 
Anova(lm(HT2$Pro_Intent_Score~HT2$Condition+HT2$Social_Desirability_Score))
Anova(lm(HT2$PBIS_score~HT2$Condition+HT2$Social_Desirability_Score))

Anova(lm(HT2$Vol_intent_combined~HT2$Condition+HT2$COVID_Stress_1))
Anova(lm(HT2$Vol_Intent_1~HT2$Condition+HT2$COVID_Stress_1))
Anova(lm(HT2$Vol_Intent_2~HT2$Condition+HT2$COVID_Stress_1))
Anova(lm(HT2$Pro_Intent_Score~HT2$Condition+HT2$COVID_Stress_1))
Anova(lm(HT2$PBIS_score~HT2$Condition+HT2$COVID_Stress_1))

summary(lm(HT2$Pro_Intent_Score~HT2$Condition+HT2$Social_Desirability_Score))
summary(lm(HT2$Vol_Intent_1~HT2$Condition+HT2$Social_Desirability_Score))
    
```